Improvement of Korean Morphological Analysis System \\Through Transformer-Based Re-Ranking

### 2023-12-12 contents/draft.tex
Add authors

    \author[1]{Author One*}
    \author[2,3]{Author Two}
    \author[3]{Author Three}
    \authormark{AUTHOR ONE \textsc{et al}}

    \address[1]{\orgdiv{Org Division}, \orgname{Org Name}, \orgaddress{\state{State name}, \country{Country name}}}
    \address[2]{\orgdiv{Org Division}, \orgname{Org Name}, \orgaddress{\state{State name}, \country{Country name}}}
    \address[3]{\orgdiv{Org Division}, \orgname{Org Name}, \orgaddress{\state{State name}, \country{Country name}}}
    \corres{*Corresponding author name, This is sample corresponding address. \email{authorone@gmail.com}}
    \presentaddress{This is sample for present address text this is sample for present address text}

@@

    \JELinfo{classification}
    \MSC{Code numbers}
    \jnlcitation{\cname{
        \author{Williams K.},
        \author{B. Hoskins},
        \author{R. Lee},
        \author{G. Masato}, and \author{T. Woollings}} (\cyear{2016}),
        \ctitle{A regime analysis of Atlantic winter jet variability applied to evaluate HadGEM3-GC2}, \cjournal{Q.J.R. Meteorol. Soc.}, \cvol{2017;00:1--6}.}
    \maketitle
    \footnotetext{\textbf{Abbreviations:} ANA, anti-nuclear antibodies; APC, antigen-presenting cells; IRF, interferon regulatory factor}

>>>>

    \author[1,2]{Jihee Ryu}
    \author[1]{Soojong Lim}
    \author[1]{Oh-Woog Kwon}
    \author[2]{Seung-Hoon Na*}
    \authormark{Jihee Ryu \textsc{et al}}

    \address[1]{\orgdiv{Language Intelligence Research Section}, \orgname{Electronics and Telecommunications Research Institute}, \orgaddress{\state{Daejeon}, \country{Republic of Korea}}}
    \address[2]{\orgdiv{Division of Computer Science and Engineering}, \orgname{Jeonbuk National University}, \orgaddress{\state{Jeollabuk-do}, \country{Republic of Korea}}}
    \corres{*Seung-Hoon Na, \orgdiv{Division of Computer Science and Engineering}, \orgname{Jeonbuk National University}, \orgaddress{\state{Jeollabuk-do}, \country{Republic of Korea}}. \email{nash@jbnu.ac.kr}}
    \presentaddress{Institute of Information \& Communications Technology Planning \& Evaluation(IITP) grant funded by the Korea government(MSIT) (RS-2023-00216011, Development of artificial complex intelligence for conceptually understanding and inferring like human)}

@@

%    \JELinfo{classification}
%    \MSC{Code numbers}
    \jnlcitation{
        \cname{
            \author{Jihee Ryu},
            \author{Soojong Lim},
            \author{Oh-Woog Kwon},
            \author{Seung-Hoon Na}
        } (\cyear{2024}),
        \ctitle{Improvement of Korean Morphological Analysis System Through Transformer-Based Re-Ranking},
        \cjournal{ETRI Journal},
        \cvol{under review}.
    }

    \maketitle
%    \footnotetext{\textbf{Abbreviations:} ANA, anti-nuclear antibodies; APC, antigen-presenting cells; IRF, interferon regulatory factor}
